A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-19 tex/codatadp.tex
got the phases a bit better now

The calculus consists of three sets of rules, given in \figuresname~\ref{fig:cc-rules} to
\ref{fig:split-rule}, corresponding to three successive phases. The first
phase computes the bidirectional closure of $\Ec$. The second phase makes
inferences based on acyclicity (for datatypes) and uniqueness (for
codatatypes). The third phase performs case splitting on constructors for
various terms in $\tEc$.
%Following the conventions from~\cite{},
%The derivation rules are given in \relax{guarded assignment form},
%where
A rule can be applied to $\Ec$ if all the specified preconditions are met.
The conclusion of a rule either describes equalities to be added to $\Ec$
or is $\bot$.
% (in which case we call an application of it \emph{nonterminal})
% (in which case we call an application of it \emph{terminal}).
A rule may have multiple conclusions separated by $\parallel$,
denoting nondeterministic branching. The rules associated with a phase are
applied until saturation (i.e., until no rule can be applied to extend~$\Ec$
further) before the next phase can begin.

@@

\paragraph{Phase 3: Branching.}
If a selector is applied to a term $t$, or if $t$'s type is a finite datatype,
the equivalence class of $t$ must contain an application of one of the constructors of $\delta$ (where $\Ctr^\delta = \{ \const{C}_1, \ldots \const{C}_m \}$).
This is enforced in the third phase by the \rn{Split} rule.
The \rn{Singleton} rule handles the degenerate case where two terms from $\tEc$
have a corecursive singleton type, in which case they must be equivalent.

>>>>

The calculus consists of three sets of rules, given in \figuresname~\ref{fig:cc-rules} to
\ref{fig:split-rule}, corresponding to three phases. The first
phase computes the bidirectional closure of $\Ec$. The second phase makes
inferences based on acyclicity (for datatypes) and uniqueness (for
codatatypes). The third phase performs case splitting on constructors for
various terms in $\tEc$.
%Following the conventions from~\cite{},
%The derivation rules are given in \relax{guarded assignment form},
%where
A rule can be applied to $\Ec$ if all the specified preconditions are met.
The conclusion of a rule either describes equalities to be added to $\Ec$
or is $\bot$.
% (in which case we call an application of it \emph{nonterminal})
% (in which case we call an application of it \emph{terminal}).
A rule may have multiple conclusions separated by $\parallel$,
denoting nondeterministic branching. The rules associated with a phase have
priority over those of the previous phases. The rules are applied until
saturation (i.e., until no rule can be applied to extend~$\Ec$
further).

@@

\paragraph{Phase 3: Branching.}
If a selector is applied to a term $t$, or if $t$'s type is a finite datatype,
the equivalence class of $t$ must contain an application of a $\delta$ constructor
(where $\Ctr^\delta = \{ \const{C}_1, \ldots, \const{C}_m \}$).
This is enforced in the third phase by the \rn{Split} rule.
A companion rule, \rn{Singleton}, handles the degenerate case where two terms
from $\tEc$ have a corecursive singleton type, in which case they must be
equivalent.
